Stochastic Wind Power Forecasting

### 2020-04-10 LaTeX_Code/Paper/paper_1line.tex
remarks

Closed-form solutions to initial-boundary value problem for SDEs can be obtained only in a few cases. Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive. 
Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations. Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.

@@

A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints which give rise to asymmetric forecasting errors as seen in figure (\ref{fig:skew_data}).\\

We propose a proxy transition density. We match the moments of our SDE model with that of the proxy density. Using It\^o formula, we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
\begin{equation}
\frac{d \mathbb{E}[ V^k_t]}{dt} = - k \theta_t \mathbb{E}[ V^k_t] + \frac{k(k-1)}{2} \mathbb{E}[ V^{k-2}_t  b(V^k_t;\theta_t, \alpha)]
\end{equation}

>>>>

Closed-form solutions to initial-boundary value problem for time-in\-ho\-mo\-geneous diffusions can be obtained only in a few cases. Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive. 
Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations. Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.

@@

Gaussian approximations to the transition densities of nonlinear time-in\-ho\-mo\-geneous SDEs are available through different algorithms  \autocite[Chapter 9]{saso}. However, as Figure (\ref{fig:error_transitions}) may suggest at a first glance, the choice of a Gaussian density could be inadequate when straightly applied to approximate the transition density of the forecast error $V$ of the normalized wind power production.

Therefore, we propose to use a surrogate transition density for $V$ other than Gaussian. The moments of the SDE model (\ref{VtSDE}) are then matched to the moments of the surrogate density.

Using It\^o's lemma on , we arrive at the following iterative ODEs for the state dependent diffusion formulation (\ref{VtSDE})
\begin{equation}
\frac{d \mathbb{E}[ V^k_t]}{dt} = - k \theta_t \mathbb{E}[ V^k_t] + \frac{k(k-1)}{2} \mathbb{E}[ V^{k-2}_t  b(V^k_t;\theta_t, \alpha)]
\end{equation}
